Navigating to a greener Europe with 24/7 hourly clean electricity procurement

### 2023-09-25 manuscript/manuscript.tex
results results, technology access
results results, diverse grid locations
suppress minor overfull hbox warnings
format: result w/o box env

@@

\newdefinition{rmk}{Remark}
\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newmdtheoremenv[
  backgroundcolor=Wheat, % Background color
  linewidth=0.5pt, % Width of the line around the box
  frametitlefont=\normalfont\bfseries, % Font for the box title
]{res}[thm]{Result}

% acronyms
\makeglossaries
\newacronym{tes}{TES}{Thermal Energy Storage (in form of water tanks)}
\newacronym{chp}{CHP}{Combined Heat and Power plant}
\newacronym{cop}{COP}{Coefficient of Performance}
\newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
\newacronym{PV}{PV}{Solar photovoltaics}
\newacronym{ghg}{GHG}{Greenhouse gas}
\newacronym{EU}{EU}{European Union}
\newacronym{dea}{DEA}{Danish Energy Agency}
\newacronym{helmeth}{HELMETH}{Integrated High-Temperature Electrolysis and Methanation for Effective Power to Gas Conversion}
\newacronym{jrc}{JRC}{Joint Research Center}
\newacronym{ocgt}{OCGT}{Open Cycle Gas Turbine}
\newacronym{v2g}{V2G}{Vehicle to Grid}
\newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
\newacronym{tyndp}{TYNDP}{Ten-Year Network Development Plan}
\newacronym{entsoe}{ENTSO-E}{European Network for Transmission System Operators for Electricity}
\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}
\newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
\newacronym{dsm}{DSM}{Demand Side Management}
\newacronym{hvdc}{HVDC}{High Voltage Direct Current}
\newacronym{phs}{PHS}{Pumped Hydro Storage}
\newacronym{dac}{DAC}{Direct Air Capture}
\newacronym{sng}{SNG}{Synthetic Natural Gas}
\newacronym{fom}{FOM}{Fixed Operation and Maintenance costs}
\newacronym{vom}{VOM}{Variable Operation and Maintenance costs}
\newacronym{ppa}{PPA}{Power Purchase Agreement}
\newacronym{ptc}{PTC}{Production Tax Credit}
\newacronym{res}{RES}{Renewable Energy Sources}
\newacronym{necp}{NECP}{National Energy and Climate Plan}
\newacronym{ets}{ETS}{Emissions Trading System}
\newacronym{capex}{CAPEX}{Capital expenditures}
\newacronym{cfd}{CfD}{Contract for Difference}
\newacronym{cfe}{CFE}{Carbon-Free Electricity}
\newacronym{ci}{C\&I}{Corporate and Industry (sectors)}

>>>>

\hfuzz=5.002pt %https://tex.stackexchange.com/questions/13715/how-to-suppress-overfull-hbox-warnings-up-to-some-maximum

@@

\newdefinition{rmk}{Remark}
\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{res}[thm]{Result}  % Result w/o box env
%\newmdtheoremenv[
%  backgroundcolor=Wheat, % Background color
%  linewidth=0.5pt, % Width of the line around the box
%  frametitlefont=\normalfont\bfseries, % Font for the box title
%]{res}[thm]{Result}

% acronyms
\makeglossaries
\newacronym{tes}{TES}{Thermal Energy Storage (in form of water tanks)}
\newacronym{chp}{CHP}{Combined Heat and Power plant}
\newacronym{cop}{COP}{Coefficient of Performance}
\newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
\newacronym{PV}{PV}{Solar photovoltaics}
\newacronym{ghg}{GHG}{Greenhouse gas}
\newacronym{EU}{EU}{European Union}
\newacronym{dea}{DEA}{Danish Energy Agency}
\newacronym{helmeth}{HELMETH}{Integrated High-Temperature Electrolysis and Methanation for Effective Power to Gas Conversion}
\newacronym{jrc}{JRC}{Joint Research Center}
\newacronym{ocgt}{OCGT}{Open Cycle Gas Turbine}
\newacronym{v2g}{V2G}{Vehicle to Grid}
\newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
\newacronym{tyndp}{TYNDP}{Ten-Year Network Development Plan}
\newacronym{entsoe}{ENTSO-E}{European Network for Transmission System Operators for Electricity}
\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}
\newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
\newacronym{dsm}{DSM}{Demand Side Management}
\newacronym{hvdc}{HVDC}{High Voltage Direct Current}
\newacronym{phs}{PHS}{Pumped Hydro Storage}
\newacronym{dac}{DAC}{Direct Air Capture}
\newacronym{sng}{SNG}{Synthetic Natural Gas}
\newacronym{fom}{FOM}{Fixed Operation and Maintenance costs}
\newacronym{vom}{VOM}{Variable Operation and Maintenance costs}
\newacronym{ppa}{PPA}{Power Purchase Agreement}
\newacronym{ptc}{PTC}{Production Tax Credit}
\newacronym{res}{RES}{Renewable Energy Sources}
\newacronym{necp}{NECP}{National Energy and Climate Plan}
\newacronym{ets}{ETS}{Emissions Trading System}
\newacronym{capex}{CAPEX}{Capital expenditures}
\newacronym{cfd}{CfD}{Contract for Difference}
\newacronym{cfe}{CFE}{Carbon-Free Electricity}
\newacronym{ci}{C\&I}{Corporate and Industry (sectors)}
\newacronym{ldes}{LDES}{Long Duration Energy Storage}
